---
title: "4th corner output"
output: html_document
# knit: (function(inputFile, encoding) {
#   rmarkdown::render(inputFile, encoding = encoding, output_dir = "/home/kunzst/Dokumente/Projects/Trait_DB/Trait-aggregation/Output/") })
params: 
  file: fc_salinity_all_traits_reduced
---

```{r, echo = FALSE}

# relevant libraries
library(reactable)
library(htmltools)

# set parameter to pick the right dataset
file <- params$file
res_fc <- readRDS(
  file.path(
    "/home/kunzst/Dokumente/Projects/Trait_DB/Trait-aggregation/Cache/Re-analysis_cache",
    paste0(file, ".rds")
  )
)

smry <- list()
for(i in names(res_fc)){
  outp <- res_fc[[i]]
  smry[[i]] <- data.frame(
    "Test" = outp$tabD2$names,
    "Obs" = round(outp$tabD2$obs, digits = 3),
    "Std.Obs" = round(outp$tabD2$expvar[, 1], digits = 3),
    "Alter" = outp$tabD2$alter,
    "Pvalue" = outp$tabD2$pvalue,
    "Pvalue.adj" = outp$tabD2$adj.pvalue
  )
}
```

### Fourth corner results with traits from Szöcs et al. 2014 study

```{r, echo = FALSE}
reactable(smry[["original"]],
            filterable = TRUE,
            highlight = TRUE)

```

### Fourth corner results harmonised but not aggregated traits

```{r, echo = FALSE}
reactable(smry[["not_aggregated"]],
            filterable = TRUE,
            highlight = TRUE)

```

### Fourth corner results with aggregated traits (stepw_median)

```{r, echo = FALSE}
reactable(smry[["stepw_median"]],
            filterable = TRUE,
            highlight = TRUE)

```

### Fourth corner results with aggregated traits (stepw_mean)

```{r, echo = FALSE}
reactable(smry[["stepw_mean"]],
            filterable = TRUE,
            highlight = TRUE)

```

### Fourth corner results with aggregated traits (direct_median)

```{r, echo = FALSE}
reactable(smry[["direct_median"]],
            filterable = TRUE,
            highlight = TRUE)

```

### Fourth corner results with aggregated traits (direct_mean)

```{r, echo = FALSE}
reactable(smry[["direct_mean"]],
            filterable = TRUE,
            highlight = TRUE)

```

### Fourth corner results with aggregated traits (weighted)

```{r, echo = FALSE}
reactable(smry[["weighted"]],
            filterable = TRUE,
            highlight = TRUE)

```

### Look-up table traits in Szöcs et al. 2014

```{r, echo = FALSE}
trait_edi_lookup <-
  fread(
    "/home/kunzst/Dokumente/Projects/Trait_DB/Trait-aggregation/Data/Edi_salinity_study/data/trait_lookup.csv",
    sep = ";"
  )
trait_edi_lookup[, ID_trait := paste0("X", ID_trait)]

reactable(trait_edi_lookup,
          filterable = TRUE,
          highlight = TRUE)
```

